---
title: "DP"
author: "Lei Shi"
date: "2024-06-28"
output: pdf_document
---

```{r}
library(dplyr)
library(ggplot2)
library(latex2exp)
source("~/Documents/GitHub/Analysis-QAP/QAPpro.R")
```


```{r}
# load the data
load("~/Documents/GitHub/Analysis-QAP/DepressionData/DP.rdata")
```


```{r}
set.seed(2024)
n = 2.5e2
rho = 0.5

# Generate data with Walsh average
R1 = rnorm(n)
R2 = rho * R1 + sqrt(1 - rho^2) * rnorm(n)
S = R1 * rnorm(n)

E = outer(1:n, 1:n, Vectorize(function(x, y) {(S[x] + S[y])/sqrt(2)}))
B1 = outer(1:n, 1:n, Vectorize(function(x, y) {(R1[x] + R1[y])/sqrt(2)}))
B2 = outer(1:n, 1:n, Vectorize(function(x, y) {(R2[x] + R2[y])/sqrt(2)}))
  
A = B2 + E
    
diag(A) = 0
diag(B1) = 0
diag(B2) = 0

data_list = list(A = A, B1 = B1, B2 = B2)
res = dyadicLM("A ~ B1 + B2", data_list)
coefs = res$coefs
var_mat = res$var_mat

coefs
var_mat
```

```{r}
QAPpro(form = "A ~ B1 + B2", 
      data_list = data_list, 
      mode = "permute-e", 
      num_perms = 100,
      var_scheme = "CR0", 
      plot.flag = F,
      nameX.target = c("B1")
      )
```

## analyze data with QAP
1 # dummy matrix at least one female 
2 # dummy matrix both female
3 # age mean (centered)
4 # age similarity # random data, for anonymity reasons
5 # one student organization # random data, for anonymity reasons
6 # same student status (being in a student organization)
7 # being friends 
8 # depression mean -> testing the depression-isolation hypothesis
9 # depression similarity -> testing the depression-homphily hypothesis
10 # depression mean * depression similarity  
11 # depression mean * being friends -> testing the depression-friendship hypothesis

```{r}
data_list = c(dvs[1], ivs[[1]][2:12])
names(data_list) = c("Y", paste0("X", 1:11))

QAP_res = QAPpro(form = "Y ~ X1 + X2 + X3 + X4 + X7 + X8 + X9 + X10 + X11", 
      data_list = data_list, 
      mode = "permute-X", 
      num_perms = 2000,
      var_scheme = "CR0", 
      plot.flag = F, 
      nameX.target = c("X8", "X9", "X10", "X11"),
      user.seed = 2024
      )
```

```{r}
QAP_res$report
```


### Depression level randomization plot
```{r}
position_x = rep(seq(-4, 4, length.out = 2000), 6)
normal_density = dnorm(position_x)
record_stat = data.frame(stat_S = QAP_res$record_perm_S[, 1],
                         position_x = position_x,
                         normal_density = normal_density)
```



```{r}
# plot permutation distribution
# hist(QAP_res$record_perm_S[, 1])

hist_plot1 = record_stat %>% ggplot(aes(x = stat_S)) +
  geom_histogram(aes(y = ..density..), col = "white", fill = "grey60", binwidth = 0.3) +
  geom_line(aes(x = position_x, y = normal_density), lty = 2) + 
  xlab(TeX(r"( $\sqrt{n}W_{Mean}^\pi$ )")) + 
  theme_classic(base_size = 20)
hist_plot1

ggsave("DPLevel.png", hist_plot1, device = "png", width = 6, height = 6)
```


### Depression similarity randomization plot
```{r}
position_x = rep(seq(-4, 4, length.out = 2000), 6)
normal_density = dnorm(position_x)
record_stat = data.frame(stat_S = QAP_res$record_perm_S[, 2],
                         position_x = position_x,
                         normal_density = normal_density)
```



```{r}
# plot permutation distribution
# hist(QAP_res$record_perm_S[, 1])

hist_plot2 = record_stat %>% ggplot(aes(x = stat_S)) +
  geom_histogram(aes(y = ..density..), col = "white", fill = "grey60", binwidth = 0.30) +
  geom_line(aes(x = position_x, y = normal_density), lty = 2) + 
  xlab(TeX(r"( $\sqrt{n}W_{Similarity}^\pi$ )")) + 
  theme_classic(base_size = 20)
hist_plot2

ggsave("DPSimilarity.png", hist_plot2, device = "png", width = 6, height = 6)
```


```{r}
data_list = c(dvs[2], ivs[[2]][2:12])
names(data_list) = c("Y", paste0("X", 1:11))

QAPpro(form = "Y ~ X1 + X2 + X3 + X4 + X7 + X8 + X9 + X10 + X11", 
      data_list = data_list, 
      mode = "permute-e", 
      num_perms = 1000,
      var_scheme = "CR0", 
      plot.flag = F, 
#       nameX.target = c("X8", "X9", "X11"),
      nameX.target = c("X8"),
      user.seed = 2024
      )
```


#### test with model 2
```{r}
data_list = c(dvs[1], ivs[[1]][2:12])
names(data_list) = c("Y", paste0("X", 1:11))

QAP_res = QAPpro(form = "Y ~ X1 + X2 + X3 + X4 + X5 + X6 + X7 + X8 + X9", 
      data_list = data_list, 
      mode = "permute-Y", 
      num_perms = 2000,
      var_scheme = "CR0", 
      plot.flag = F, 
      nameX.target = paste0("X", 8:9),
      user.seed = 2024
      )
```
```{r}
QAP_res$report
```

```{r}
position_x = rep(seq(-4, 4, length.out = 2000), 6)
normal_density = dnorm(position_x)
record_stat = data.frame(stat_S = QAP_res$record_perm_S[, 1],
                         position_x = position_x,
                         normal_density = normal_density)
```



```{r}
# plot permutation distribution
# hist(QAP_res$record_perm_S[, 1])

record_stat %>% ggplot(aes(x = stat_S)) +
  geom_histogram(aes(y = ..density..), col = "white", fill = "grey60", binwidth = 0.25) +
  geom_line(aes(x = position_x, y = normal_density), lty = 2) + 
  xlab(TeX(r"( $\sqrt{n}\hat{\vartheta}$ )")) + 
  theme_classic(base_size = 20)
```